Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-3\baselineskip}

### 2017-03-20 paper/ms.tex
minor edits section 5

We now turn to the application of the \celerite\ algorithm to astrophysical
variability.  Many astrophysical objects have a characteristic timescale
of variability which is determined by its physical structure. The variability
is excited by noisy physical processes, but also damped due to dissipation 
in the system.  As a concrete example, stellar oscillations are strong at 
resonant frequencies determined by the internal stellar structure,
which are excited and damped by convective turbulence.

@@

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{figures/sho.pdf}
\caption{(left) The power spectrum of a stochastically-driven simple harmonic
    oscillator (\eqalt{sho-psd}) plotted for several values of the quality
    factor $Q$.
    For comparison, the dashed line shows the Lorentzian function from
    \eq{lorentz-psd} with $c_j = \omega_0/2\,Q = 1/20$ and normalized so that
    $S(d_j)/S(0) = 100$.
    (right) The corresponding autocorrelation functions with the same colors.
    \figurelabel{sho}}
\end{center}
\end{figure}

>>>>

We now turn to the application of the \celerite\ algorithm to astrophysical
variability.  Many astronomical objects have a characteristic timescale
which is determined by the physical structure.  Variability
is excited by noisy physical processes, which grows most strongly at
the characteristic timescale, but is also damped due to dissipation 
in the system.  As a concrete example, stellar oscillations are strong at 
resonant frequencies determined by the internal stellar structure,
which are both excited and damped by convective turbulence.

@@

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{figures/sho.pdf}
\caption{(left) The power spectrum of a stochastically-driven simple harmonic
    oscillator (\eqalt{sho-psd}) plotted for several values of the quality
    factor $Q$.
    For comparison, the dashed line shows the Lorentzian function from
    \eq{lorentz-psd} with $c_j = \omega_0/(2\,Q) = 1/20$ and normalized so that
    $S(d_j)/S(0) = 100$.
    (right) The corresponding autocorrelation functions with the same colors.
    \figurelabel{sho}}
\end{center}
\end{figure}
